
\chapwithtoc{Conclusion}

In this thesis, we explored the applications of graph neural networks and deep reinforcement learning to job-shop scheduling.\\
In \textbf{Chapter 1}, we defined the job scheduling problem, flexible job shop scheduling problem, and dynamic job shop scheduling problem. We also presented priority dispatching rules as a computationally fast and intuitive heuristic, and we discussed how reinforcement learning helps automate the process of designing priority dispatching rules.\\
In \textbf{Chapter 2}, we introduced the concept of graph neural networks and deep reinforcement learning. We presented different neural architectures and algorithms for training them.\\
In \textbf{Chapter 3}, we presented five publicly available models from GitHub, four of which have been published in the literature. We described their input features, their architecture, and their training algorithms. We also presented our extension of three of these models to dynamic job shop scheduling.\\
In \textbf{Chapter 4}, we presented the setup of our experiment, in which we tested all models on the same benchmark instances. Then, we presented the results of our experiment for different job shop scheduling variants.\\
In \textbf{Chapter 5}, we discussed our results. Our findings indicate that the feature selection for the neural network is more important than the network architecture. We also discussed which features may be important for each job shop scheduling variant.\\
In conclusion, this thesis presented an experimental overview and comparison of publicly available models for solving job shop scheduling using graph neural networks and deep reinforcement learning. It also lays the foundation for future research in this area.